---
title: "Question 1"
---


```{r, message = FALSE}
library(tidyverse)
```

You are required to use the functional programming approach to solve the following problems.


First we prepare some files to work with.
The `walk` function is very similar to the `map` function except that it doesn't return values.


```{r}
dir.create("files", showWarnings = FALSE)
set.seed(141)
1:100 %>% walk(function(i) {
    dt <- tibble(x = rnorm(10), y = rnorm(10))
    write_csv(dt, file.path("files", sprintf("file%02d.csv", i)))
})
```

##### (a) Read the csv files using `Sys.glob("files/*")`, `map` and `read_csv`. Save the result as `ll`.

Remark: to suppress messages from running `read_csv`, consider `col_types = "dd"`.




##### (b) Use `ll` and `map_dbl` to compute 20% trimmed mean of the variable `x` for each dataset (Don't print the answers!)


##### (c) Use `ll` `map` and `t.test` to run a t test to check the equality of `mean(x)` and `mean(y)` for each file. (Don't print the answers!)



##### (d) Extract the $p$-values in part(c) and plot a histogram of the $p$-values. What shape the distribution is it?



##### (e) We want to make sure that `mean(x)` must be less than `mean(y)` by swapping the values of `x` and `y` if `mean(y) <= mean(x).` Use `map_if` to perform this operation.

